\ttitle

### 2015-08-23 Appendices/AppendixAccessDatabase.tex
Review - Minor changes to Appendices
- Modify short title
- insert \clearpage

\chapter{Visual Basic for Applications For Data Collection} % Main appendix title
\label{AppendixAccessDatabase} % For referencing this appendix elsewhere, use \ref{AppendixA}
\lhead{Appendix \ref{AppendixAccessDatabase}. \emph{MS Access VBA For Data Collection}} % This is for the header on each page - perhaps a shortened title

\setstretch{1.0}
%------------------------------------------

>>>>

\chapter{Visual Basic for Applications For Data Collection}
\label{AppendixAccessDatabase}
\lhead{Appendix \ref{AppendixAccessDatabase}. \emph{MS Access VBA For Data Collection}}
\clearpage
%------------------------------------------

\setstretch{1.0}
